---
title: "A Computational Analysis of the Business Media's Response to Covid-19: Quantitive Numeric Analysis"
author: "Caryn Biebuyck (20715978) & Lauren Downing (19202113)"
output: html_notebook
---


```{r Setup, message=FALSE, warning=FALSE, include=FALSE}
  library(dplyr)
  library(ggplot2)
  library(ggraph)
  library(igraph)
  library(scales)
  library(stringr)
  library(tidyr)
  library(tidytext)
  library(widyr)
  library(wordcloud)
```

```{r Reading in required RDS files, message=FALSE, warning=FALSE, include=FALSE}
  fin24 <- readRDS("~/tidy_fin24.rds")
  moneyweb <- readRDS("~/tidy_moneyweb.rds")
  biznews <- readRDS("~/tidy_biznews.rds")
  EWNbusiness <- readRDS("~/tidy_ewn.rds")
  businessTech <- readRDS("~/tidy_businesstech.rds")
  mediaCompiled <- readRDS("~/tidy_mediacompiled.rds")
```


# 1. Word Counts

## 1.1. Fin24
```{r Fin24 Top Words}
  fin24_topWords <- fin24 %>%
    count(word) %>%
    arrange(desc(n))

  fin24_topWords
  
# Visualisation of top 25 words
  fin24_topWords_visual <- fin24_topWords %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -n), y = n, fill = word)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("Frequency") +
    scale_y_continuous(breaks = seq(0, 1000, 100)) +
    xlab("") +
    labs(title = "Most frequented words", subtitle = "Fin24") +
    guides(fill = FALSE)
  
  fin24_topWords_visual
  
# Save the graph to disk  
  ggsave(fin24_topWords_visual, filename = "fin24_topWords_visual.png", width = 185, height = 114, units = "mm")
```
  
## 1.2. Moneyweb
```{r Moneyweb Top Words}
  moneyweb_topWords <- moneyweb %>%
    count(word) %>%
    arrange(desc(n))

  moneyweb_topWords
  
# Visualisation of top 25 words
  moneyweb_topWords_visual <- moneyweb_topWords %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -n), y = n, fill = word)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    scale_y_continuous(breaks = seq(0, 1400, 100)) +
    ylab("Frequency") +
    xlab("") +
    labs(title = "Most frequented words", subtitle = "Moneyweb") +
    guides(fill = FALSE)
  
  moneyweb_topWords_visual
  
# Save the graph to disk  
  ggsave(moneyweb_topWords_visual, filename = "moneyweb_topWords_visual.png", width = 185, height = 114, units = "mm")
```
  
## 1.3. BizNews
```{r BizNews Top Words}
  biznews_topWords <- biznews %>%
    count(word) %>%
    arrange(desc(n))

  biznews_topWords
  
# Visualisation of top 25 words
  biznews_topWords_visual <- biznews_topWords %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -n), y = n, fill = word)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("Frequency") +
    scale_y_continuous(breaks = seq(0, 1000, 100)) +
    xlab("") +
    labs(title = "Most frequented words", subtitle = "BizNews") +
    guides(fill = FALSE)
  
  biznews_topWords_visual
  
# Save the graph to disk  
  ggsave(biznews_topWords_visual, filename = "biznews_topWords_visual.png", width = 185, height = 114, units = "mm")
```

## 1.4. EWN Business 
```{r EWN Business Top Words}
  EWNbusiness_topWords <- EWNbusiness %>%
    count(word) %>%
    arrange(desc(n))

  EWNbusiness_topWords
  
# Visualisation of top 25 words
  EWNbusiness_topWords_visual <- EWNbusiness_topWords %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -n), y = n, fill = word)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("Frequency") +
    scale_y_continuous(breaks = seq(0, 4000, 250)) +
    xlab("") +
    labs(title = "Most frequented words", subtitle = "EWN Business") +
    guides(fill = FALSE)
  
  EWNbusiness_topWords_visual
  
# Save the graph to disk  
  ggsave(EWNbusiness_topWords_visual, filename = "EWNbusiness_topWords_visual.png", width = 185, height = 114, units = "mm")
```
  
## 1.5. BusinessTech
```{r BusinessTech Top Words}
  businessTech_topWords <- businessTech %>%
    count(word) %>%
    arrange(desc(n))

  businessTech_topWords
  
# Visualisation of top 25 words
  businessTech_topWords_visual <- businessTech_topWords %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -n), y = n, fill = word)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("Frequency") +
    scale_y_continuous(breaks = seq(0, 4000, 250)) +
    xlab("") +
    labs(title = "Most frequented words", subtitle = "BusinessTech") +
    guides(fill = FALSE)
  
  businessTech_topWords_visual
  
# Save the graph to disk  
  ggsave(businessTech_topWords_visual, filename = "businessTech_topWords_visual.png", width = 185, height = 114, units = "mm")
```
  
## 1.6. Across All Media Outlets 
```{r Compiled Media Top Words}
  mediaCompiled_topWords <- mediaCompiled %>%
    count(word) %>%
    arrange(desc(n))

  mediaCompiled_topWords
  
# Visualisation of top 25 words
  mediaCompiled_topWords_visual <- mediaCompiled_topWords %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -n), y = n, fill = word)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("Frequency") +
    scale_y_continuous(breaks = seq(0, 10000, 500)) +
    xlab("") +
    labs(title = "Most frequented words", subtitle = "All media outlets") +
    guides(fill = FALSE)
    
  mediaCompiled_topWords_visual
  
# Save the graph to disk  
  ggsave(mediaCompiled_topWords_visual, filename = "mediaCompiled_topWords_visual.png", width = 185, height = 114, units = "mm")
```

## 1.7. Comparing Media Outlets, Using EWN Business as a Basis (due to EWN Business having has the most overall words)

### 1.7.1. EWN Business vs Fin24
```{r EWN Business vs Fin24}
 fin24vsEWN <- bind_rows(mutate(fin24, media.source = "Fin24"),  
                         mutate(EWNbusiness, media.source = "EWN Business")) %>%
    mutate(word = str_extract(word, "[a-z']+")) %>%
    count(media.source, word) %>%
    group_by(media.source) %>%
    mutate(proportion = n/sum(n)) %>%
    select(-n) %>%
    spread(media.source, proportion) %>%
    gather(media.source, proportion, Fin24)
  
 fin24vsEWN 
 
# Visualisation 
  fin24vsEWN_visual <- ggplot(fin24vsEWN, aes(x = proportion, y = `EWN Business`, color = abs(`EWN Business` - proportion))) +
    geom_abline(color = "grey60", lty = 2) +
    geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
    geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
    scale_x_log10(labels = percent_format()) +
    scale_y_log10(labels = percent_format()) +
    scale_color_gradient(limits = c(0, 0.001), low = "grey20", high = "grey75") +
    facet_wrap(~media.source, ncol = 2) +
    theme_minimal() +
    theme(legend.position = "none") +
    labs(y = "EWN business", x = NULL)
  
  fin24vsEWN_visual
  
# Save the graph to disk  
  ggsave(fin24vsEWN_visual, filename = "fin24vsEWN_visual.png", width = 185, height = 114, units = "mm")
  
# Correlation Test
  cor.test(data = fin24vsEWN[fin24vsEWN$media.source == "Fin24",],
           ~proportion + `EWN Business`)
```

### 1.7.2. EWN Business vs Moneyweb
```{r EWN Business vs Moneyweb}
 moneywebVsEWN <- bind_rows(mutate(moneyweb, media.source = "Moneyweb"),  
                            mutate(EWNbusiness, media.source = "EWN Business")) %>%
    mutate(word = str_extract(word, "[a-z']+")) %>%
    count(media.source, word) %>%
    group_by(media.source) %>%
    mutate(proportion = n/sum(n)) %>%
    select(-n) %>%
    spread(media.source, proportion) %>%
    gather(media.source, proportion, Moneyweb)
  
 moneywebVsEWN 
 
# Visualisation 
  moneywebVsEWN_visual <- ggplot(moneywebVsEWN, aes(x = proportion, y = `EWN Business`, color = abs(`EWN Business` - proportion))) +
    geom_abline(color = "grey60", lty = 2) +
    geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
    geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
    scale_x_log10(labels = percent_format()) +
    scale_y_log10(labels = percent_format()) +
    scale_color_gradient(limits = c(0, 0.001), low = "grey20", high = "grey75") +
    facet_wrap(~media.source, ncol = 2) +
    theme_minimal() +
    theme(legend.position = "none") +
    labs(y = "EWN business", x = NULL)
  
  moneywebVsEWN_visual
  
# Save the graph to disk  
  ggsave(moneywebVsEWN_visual, filename = "moneywebVsEWN_visual.png", width = 185, height = 114, units = "mm")
  
# Correlation Test
  cor.test(data = moneywebVsEWN[moneywebVsEWN$media.source == "Moneyweb",],
           ~proportion + `EWN Business`)
```
  
### 1.7.3. EWN Business vs BizNews
```{r EWN Business vs BizNews}
 biznewsVsEWN <- bind_rows(mutate(biznews, media.source = "BizNews"),  
                            mutate(EWNbusiness, media.source = "EWN Business")) %>%
    mutate(word = str_extract(word, "[a-z']+")) %>%
    count(media.source, word) %>%
    group_by(media.source) %>%
    mutate(proportion = n/sum(n)) %>%
    select(-n) %>%
    spread(media.source, proportion) %>%
    gather(media.source, proportion, BizNews)
  
  biznewsVsEWN 
 
# Visualisation 
   biznewsVsEWN_visual <- ggplot(biznewsVsEWN, aes(x = proportion, y = `EWN Business`, color = abs(`EWN Business` - proportion))) +
    geom_abline(color = "grey60", lty = 2) +
    geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
    geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
    scale_x_log10(labels = percent_format()) +
    scale_y_log10(labels = percent_format()) +
    scale_color_gradient(limits = c(0, 0.001), low = "grey20", high = "grey75") +
    facet_wrap(~media.source, ncol = 2) +
    theme_minimal() +
    theme(legend.position = "none") +
    labs(y = "EWN business", x = NULL)
  
   biznewsVsEWN_visual
   
# Save the graph to disk  
  ggsave(biznewsVsEWN_visual, filename = "biznewsVsEWN_visual.png", width = 185, height = 114, units = "mm")
  
# Correlation Test
  cor.test(data =  biznewsVsEWN[biznewsVsEWN$media.source == "BizNews",],
           ~proportion + `EWN Business`)
```
  
### 1.7.4. EWN Business vs BusinessTech
```{r EWN Business vs BusinessTech}
 businessTechVsEWN <- bind_rows(mutate(businessTech, media.source = "BusinessTech"),  
                            mutate(EWNbusiness, media.source = "EWN Business")) %>%
    mutate(word = str_extract(word, "[a-z']+")) %>%
    count(media.source, word) %>%
    group_by(media.source) %>%
    mutate(proportion = n/sum(n)) %>%
    select(-n) %>%
    spread(media.source, proportion) %>%
    gather(media.source, proportion, BusinessTech)
  
  businessTechVsEWN 
 
# Visualisation 
  businessTechVsEWN_visual <- ggplot(businessTechVsEWN, aes(x = proportion, y = `EWN Business`, color = abs(`EWN Business` - proportion))) +
    geom_abline(color = "grey60", lty = 2) +
    geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
    geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
    scale_x_log10(labels = percent_format()) +
    scale_y_log10(labels = percent_format()) +
    scale_color_gradient(limits = c(0, 0.001), low = "grey20", high = "grey75") +
    facet_wrap(~media.source, ncol = 2) +
    theme_minimal() +
    theme(legend.position = "none") +
    labs(y = "EWN business", x = NULL)
  
  businessTechVsEWN_visual
  
# Save the graph to disk  
  ggsave(businessTechVsEWN_visual, filename = "businessTechVsEWN_visual.png", width = 185, height = 114, units = "mm")
  
# Correlation Test
  cor.test(data =  businessTechVsEWN[businessTechVsEWN$media.source == "BusinessTech",],
           ~proportion + `EWN Business`)
```

# 2. Wordclouds

## 2.1. Fin24
```{r Wordcloud: Fin24}
  fin24_wordcloud <- fin24 %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))

  fin24_wordcloud
```
  
## 2.2. Moneyweb
```{r Wordcloud: Moneyweb}
  moneyweb_wordcloud <- moneyweb %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))

  moneyweb_wordcloud
```
  
## 2.3. BizNews
```{r Wordcloud: BizNews}
  biznews_wordcloud <- biznews %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))

  biznews_wordcloud
```
  
## 2.4. EWN Business
```{r Wordcloud: EWN Business}
  EWNbusiness_wordcloud <- EWNbusiness %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))

  EWNbusiness_wordcloud
```
  
## 2.5. BusinessTech
```{r Wordcloud: BusinessTech}
  businessTech_wordcloud <- businessTech %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))

  businessTech_wordcloud
```
  
## 2.6. Across All Media Outlets
```{r Wordcloud: Compiled Media}
  mediaCompiled_wordcloud <- mediaCompiled %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))

  mediaCompiled_wordcloud
```
  
# 3. Term Frequency Inverse Document Frequency

## 3.1. Fin24
```{r TF-IDF: Fin24}
  fin24_tfidf <- fin24 %>%
    count(word, date) %>%
    bind_tf_idf(word, date, n)

  fin24_tfidf
  
  fin24_top_tfidf <- fin24_tfidf %>%
    arrange(desc(tf_idf))
  
  fin24_top_tfidf
  
# Visualisation of top 25 TF-IDFs
  fin24_top_tfidf_visual <- fin24_top_tfidf %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -tf_idf), y = tf_idf, fill = date)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("TF-IDF") +
    scale_y_continuous(breaks = seq(0, 0.3, 0.05)) +
    xlab("") +
    labs(title = "Highest TF-IDF words", subtitle = "Fin24") +
    guides(fill = guide_legend(title = "Date"))
    
    
  fin24_top_tfidf_visual
  
# Save the graph to disk  
  ggsave(fin24_top_tfidf_visual, filename = "fin24_top_tfidf_visual.png", width = 185, height = 114, units = "mm")
```
  
## 3.2. Moneyweb
```{r TF-IDF: Moneyweb}
 moneyweb_tfidf <- moneyweb %>%
    count(word, date) %>%
    bind_tf_idf(word, date, n)

  moneyweb_tfidf
  
  moneyweb_top_tfidf <- moneyweb_tfidf %>%
    arrange(desc(tf_idf))
  
  moneyweb_top_tfidf
  
# Visualisation of top 25 TF-IDFs
   moneyweb_top_tfidf_visual <- moneyweb_top_tfidf %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -tf_idf), y = tf_idf, fill = date)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("TF-IDF") +
    scale_y_continuous(breaks = seq(0, 0.3, 0.05)) +
    xlab("") +
    labs(title = "Highest TF-IDF words", subtitle = "Moneyweb") +
    guides(fill = guide_legend(title = "Date"))
    
  moneyweb_top_tfidf_visual
  
# Save the graph to disk  
  ggsave(moneyweb_top_tfidf_visual, filename = "moneyweb_top_tfidf_visual.png", width = 185, height = 114, units = "mm")
```
  
## 3.3. BizNews
```{r TF-IDF: BizNews}
 biznews_tfidf <- biznews %>%
    count(word, date) %>%
    bind_tf_idf(word, date, n)

 biznews_tfidf
  
 biznews_top_tfidf <- biznews_tfidf %>%
    arrange(desc(tf_idf)) %>%
    mutate(word = factor(word, levels = rev(unique(word)))) %>%
    group_by(date) %>% 
    top_n(25) %>% 
    ungroup() 
  
  biznews_top_tfidf
  
# Visualisation of top 25 TF-IDFs
  biznews_top_tfidf_visual <- biznews_top_tfidf %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -tf_idf), y = tf_idf, fill = date)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("TF-IDF") +
    scale_y_continuous(breaks = seq(0, 0.3, 0.05)) +
    xlab("") +
    ggtitle("Highest TF-IDF words", subtitle = "Biznews") +
    guides(fill = guide_legend(title = "Date"))
  
  biznews_top_tfidf_visual
  
# Save the graph to disk  
  ggsave(biznews_top_tfidf_visual, filename = "biznews_top_tfidf_visual.png", width = 185, height = 114, units = "mm")
```
  
## 3.4. EWN Business
```{r TF-IDF: EWN Business}
 EWNbusiness_tfidf <- EWNbusiness %>%
    count(word, date) %>%
    bind_tf_idf(word, date, n)

 EWNbusiness_tfidf
  
 EWNbusiness_top_tfidf <- EWNbusiness_tfidf %>%
    arrange(desc(tf_idf))
  
  EWNbusiness_top_tfidf
  
# Visualisation of top 25 TF-IDFs
EWNbusiness_top_tfidf_visual <- EWNbusiness_top_tfidf %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -tf_idf), y = tf_idf, fill = date)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("TF-IDF") +
    scale_y_continuous(breaks = seq(0, 0.3, 0.025)) +
    xlab("") +
    labs(title = "Highest TF-IDF words", subtitle = "EWN Business") +
    guides(fill = guide_legend(title = "Date"))

  EWNbusiness_top_tfidf_visual
  
# Save the graph to disk  
  ggsave(EWNbusiness_top_tfidf_visual, filename = "EWNbusiness_top_tfidf_visual.png", width = 185, height = 114, units = "mm")
```
  
## 3.5. BusinessTech
```{r TF-IDF: BusinessTech}
  businessTech_tfidf <- businessTech %>%
    count(word, date) %>%
    bind_tf_idf(word, date, n)

 businessTech_tfidf
  
 businessTech_top_tfidf <- businessTech_tfidf %>%
    arrange(desc(tf_idf))
  
  businessTech_top_tfidf
  
# Visualisation of top 25 TF-IDFs
  businessTech_top_tfidf_visual <- businessTech_top_tfidf %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -tf_idf), y = tf_idf, fill = date)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("TF-IDF") +
    scale_y_continuous(breaks = seq(0, 0.3, 0.05)) +
    xlab("") +
    labs(title = "Highest TF-IDF words", subtitle = "BusinessTech") +
    guides(fill = guide_legend(title = "Date"))
    
  businessTech_top_tfidf_visual
  
# Save the graph to disk  
  ggsave(businessTech_top_tfidf_visual, filename = "businessTech_top_tfidf_visual.png", width = 185, height = 114, units = "mm")
```
  
## 3.6. Across All Media Outlets
```{r TF-IDF: Compiled Media}
 mediaCompiled_tfidf <- mediaCompiled %>%
    count(word, date) %>%
    bind_tf_idf(word, date, n)

 mediaCompiled_tfidf
  
 mediaCompiled_top_tfidf <- mediaCompiled_tfidf %>%
    arrange(desc(tf_idf))
  
  mediaCompiled_top_tfidf
  
# Visualisation of top 25 TF-IDFs
  mediaCompiled_top_tfidf_visual <- mediaCompiled_top_tfidf %>%
    slice(1:25) %>%
    ggplot(aes(x = reorder(word, -tf_idf), y = tf_idf, fill = date)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
          plot.title = element_text(hjust = 0.5, size = 18)) +
    ylab("TF-IDF") +
    scale_y_continuous(breaks = seq(0, 0.3, 0.01)) +
    xlab("") +
    labs(title = "Highest TF-IDF words", subtitle = "All media outlets") +
    guides(fill = guide_legend(title = "Date"))
    
  mediaCompiled_top_tfidf_visual
  
# Save the graph to disk  
  ggsave(mediaCompiled_top_tfidf_visual, filename = "mediaCompiled_top_tfidf_visual.png", width = 185, height = 114, units = "mm")
```
  
# 4. Counting and Correlating Pairs of Words with `widyr`

## 4.1. Fin24

### 4.1.1. Word Pairs
```{r Word Pairs: Fin24}
  fin24_wordPairs <- fin24 %>%
    pairwise_count(word, title, sort = TRUE)

  fin24_wordPairs
  
# Pairwise correlation
  fin24_wordPairs_cor <- fin24 %>%
    group_by(word) %>%
    filter(n() >= 20) %>% # Filtering for relatively common words
    pairwise_cor(word, title, sort = TRUE)
  
  fin24_wordPairs_cor
  
# Filtering for words most associated with the Covid-19 pandemic
  fin24_covid_cor <- fin24_wordPairs_cor %>%
    filter(item1 %in% c("ban", "covid", "lockdown")) %>%
    mutate(item2 = reorder(item2, correlation)) 
    
  fin24_covid_cor
  
# Visualising the 10 most associated words 
  fin24_covid_cor_visual <-  fin24_covid_cor %>%
    group_by(item1) %>%
    top_n(10) %>%
    ungroup() %>%
    ggplot(aes(reorder(item2, correlation), correlation)) +
      geom_bar(stat = "identity", fill = "royalblue2") +
      labs(title = "10 most associated words", subtitle = "Fin24", x = "Associated words") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
            plot.title = element_text(size = 18),
            plot.subtitle = element_text(color = "grey40")) +
      facet_wrap(~item1, scales = "free") +
      coord_flip()
  
  fin24_covid_cor_visual
  
# Save the graph to disk  
  ggsave(fin24_covid_cor_visual, filename = "fin24_covid_cor_visual.png", width = 185, height = 114, units = "mm")
```

4.1.2. Word Clusters
```{r Word Clusters: Fin24}
# ggraph visualisation of the correlations and word clusters for the top 20 Covid-19-oriented word pairs
fin24_covid_ggraph <- fin24_covid_cor %>%
    group_by(item1) %>%
    top_n(20) %>%
    ungroup() %>%
    filter(correlation > .15) %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
    geom_node_point(color = "royalblue2", size = 5) +
    geom_node_text(aes(label = unique(name)), repel = TRUE) +
    labs(title = "Word clusters", subtitle = "Fin24") +
    theme_void() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"))
  
  fin24_covid_ggraph
  
# Save the graph to disk  
  ggsave(fin24_covid_ggraph, filename = "fin24_covid_ggraph.png", width = 185, height = 114, units = "mm")
```
  
## 4.2. Moneyweb

### 4.2.1. Word Pairs
```{r Word Pairs: Moneyweb}
  moneyweb_wordPairs <- moneyweb %>%
    pairwise_count(word, title, sort = TRUE)

  moneyweb_wordPairs
  
# Pairwise correlation
  moneyweb_wordPairs_cor <- moneyweb %>%
    group_by(word) %>%
    filter(n() >= 20) %>% # Filtering for relatively common words
    pairwise_cor(word, title, sort = TRUE)
  
  moneyweb_wordPairs_cor
  
# Filtering for words most associated with the Covid-19 pandemic 
  moneyweb_covid_cor <- moneyweb_wordPairs_cor %>%
    filter(item1 %in% c("ban", "covid", "lockdown")) %>%
    mutate(item2 = reorder(item2, correlation)) 
    
  moneyweb_covid_cor 
  
# Visualising the 10 most associated words 
  moneyweb_covid_cor_visual <-  moneyweb_covid_cor %>%
    group_by(item1) %>%
    top_n(10) %>%
    ungroup() %>%
    ggplot(aes(reorder(item2, correlation), correlation)) +
      geom_bar(stat = "identity", fill = "royalblue2") +
      labs(title = "10 most associated words", subtitle = "Moneyweb", x = "Associated words") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
            plot.title = element_text(size = 18),
            plot.subtitle = element_text(color = "grey40")) +
      facet_wrap(~item1, scales = "free") +
      coord_flip()
  
  moneyweb_covid_cor_visual
  
# Save the graph to disk  
  ggsave(moneyweb_covid_cor_visual, filename = "moneyweb_covid_cor_visual.png", width = 185, height = 114, units = "mm")
```

### 4.2.2 Word Clusters
```{r Word Clusters: Moneyweb}
# ggraph visualisation of the correlations and word clusters for the top 20 Covid-19-oriented word pairs
  moneyweb_covid_ggraph <- moneyweb_covid_cor %>%
    group_by(item1) %>%
    top_n(20) %>%
    ungroup() %>%
    filter(correlation > .15) %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
    geom_node_point(color = "royalblue2", size = 5) +
    geom_node_text(aes(label = unique(name)), repel = TRUE) +
    labs(title = "Word clusters", subtitle = "Moneyweb") +
    theme_void() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"))
  
  moneyweb_covid_ggraph
  
# Save the graph to disk  
  ggsave(moneyweb_covid_ggraph, filename = "moneyweb_covid_ggraph.png", width = 185, height = 114, units = "mm")
```
  
## 4.3. BizNews

### 4.3.1. Word Pairs
```{r Word Pairs: BizNews}
 biznews_wordPairs <- biznews %>%
    pairwise_count(word, title, sort = TRUE)

  biznews_wordPairs
  
# Pairwise correlation
  biznews_wordPairs_cor <- biznews %>%
    group_by(word) %>%
    filter(n() >= 20) %>% # Filtering for relatively common words
    pairwise_cor(word, title, sort = TRUE)
  
  biznews_wordPairs_cor
  
# Filtering for words most associated with the Covid-19 pandemic 
  biznews_covid_cor <- biznews_wordPairs_cor %>%
    filter(item1 %in% c("ban", "covid", "lockdown")) %>%
    mutate(item2 = reorder(item2, correlation)) 
    
  biznews_covid_cor 
  
# Visualising the 10 most associated words 
  biznews_covid_cor_visual <-  biznews_covid_cor %>%
    group_by(item1) %>%
    top_n(10) %>%
    ungroup() %>%
    ggplot(aes(reorder(item2, correlation), correlation)) +
      geom_bar(stat = "identity", fill = "royalblue2") +
      labs(title = "10 most associated words", subtitle = "BizNews", x = "Associated words") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
            plot.title = element_text(size = 18),
            plot.subtitle = element_text(color = "grey40")) +
      facet_wrap(~item1, scales = "free") +
      coord_flip()
  
  biznews_covid_cor_visual
  
# Save the graph to disk  
  ggsave(biznews_covid_cor_visual, filename = "biznews_covid_cor_visual.png", width = 185, height = 114, units = "mm")
```

### 4.3.2. Word Clusters
```{r Word Clusters: BizNews}
# ggraph visualisation of the correlations and word clusters for the top 20 Covid-19-oriented word pairs
  biznews_covid_ggraph <- biznews_covid_cor %>%
    group_by(item1) %>%
    top_n(20) %>%
    ungroup() %>%
    filter(correlation > .15) %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
    geom_node_point(color = "royalblue2", size = 5) +
    geom_node_text(aes(label = name), repel = TRUE) +
    labs(title = "Word clusters", subtitle = "BizNews") +
    theme_void() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"))
  
  biznews_covid_ggraph
  
# Save the graph to disk  
  ggsave(biznews_covid_ggraph, filename = "biznews_covid_ggraph.png", width = 185, height = 114, units = "mm")
```
  
## 4.4. EWN Business

### 4.4.1. Word Pairs
```{r Word Pairs: EWN Business}
  EWNbusiness_wordPairs <- EWNbusiness %>%
    pairwise_count(word, title, sort = TRUE)

  EWNbusiness_wordPairs
  
# Pairwise correlation
  EWNbusiness_wordPairs_cor <- EWNbusiness %>%
    group_by(word) %>%
    filter(n() >= 20) %>% # Filtering for relatively common words
    pairwise_cor(word, title, sort = TRUE)
  
  EWNbusiness_wordPairs_cor
  
# Filtering for words most associated with the Covid-19 pandemic 
  EWNbusiness_covid_cor <- EWNbusiness_wordPairs_cor %>%
    filter(item1 %in% c("ban", "covid", "lockdown")) %>%
    mutate(item2 = reorder(item2, correlation)) 
    
  EWNbusiness_covid_cor 
  
# Visualising the 10 most associated words 
  EWNbusiness_covid_cor_visual <-  EWNbusiness_covid_cor %>%
    group_by(item1) %>%
    top_n(10) %>%
    ungroup() %>%
    ggplot(aes(reorder(item2, correlation), correlation)) +
      geom_bar(stat = "identity", fill = "royalblue2") +
      labs(title = "10 most associated words", subtitle = "EWN Business", x = "Associated words") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
            plot.title = element_text(size = 18),
            plot.subtitle = element_text(color = "grey40")) +
      facet_wrap(~item1, scales = "free") +
      coord_flip()
  
  EWNbusiness_covid_cor_visual
  
# Save the graph to disk  
  ggsave(EWNbusiness_covid_cor_visual, filename = "EWNbusiness_covid_cor_visual.png", width = 185, height = 114, units = "mm")
```

### 4.4.2. Word Clusters
```{r Word Clusters: EWN Business}
# ggraph visualisation of the correlations and word clusters for the top 20 covid-oriented word pairs
  EWNbusiness_covid_ggraph <- EWNbusiness_covid_cor %>%
    group_by(item1) %>%
    top_n(20) %>%
    ungroup() %>%
    filter(correlation > .15) %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
    geom_node_point(color = "royalblue2", size = 5) +
    geom_node_text(aes(label = name), repel = TRUE) +
    labs(title = "Word clusters", subtitle = "EWN Business") +
    theme_void() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"))
  
  EWNbusiness_covid_ggraph
  
# Save the graph to disk  
  ggsave(EWNbusiness_covid_ggraph, filename = "EWNbusiness_covid_ggraph.png", width = 185, height = 114, units = "mm")
```
  
## 4.5. BusinessTech

### 4.5.1. Word Pairs
```{r Word Pairs: BusinessTech}
  businessTech_wordPairs <- businessTech %>%
    pairwise_count(word, title, sort = TRUE)

  businessTech_wordPairs
  
# Pairwise correlation
  businessTech_wordPairs_cor <- businessTech %>%
    group_by(word) %>%
    filter(n() >= 20) %>% # Filtering for relatively common words
    pairwise_cor(word, title, sort = TRUE)
  
  businessTech_wordPairs_cor
  
# Filtering for words most associated with the Covid-19 pandemic 
  businessTech_covid_cor <- businessTech_wordPairs_cor %>%
    filter(item1 %in% c("ban", "covid", "lockdown")) %>%
    mutate(item2 = reorder(item2, correlation)) 
    
  businessTech_covid_cor 
  
# Visualising the 10 most associated words 
  businessTech_covid_cor_visual <-  businessTech_covid_cor %>%
    group_by(item1) %>%
    top_n(10) %>%
    ungroup() %>%
    ggplot(aes(reorder(item2, correlation), correlation)) +
      geom_bar(stat = "identity", fill = "royalblue2") +
      labs(title = "10 most associated words", subtitle = "BusinessTech", x = "Associated words") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
            plot.title = element_text(size = 18),
            plot.subtitle = element_text(color = "grey40")) +
      facet_wrap(~item1, scales = "free") +
      coord_flip()
  
  businessTech_covid_cor_visual
  
# Save the graph to disk  
  ggsave(businessTech_covid_cor_visual, filename = "businessTech_covid_cor_visual.png", width = 185, height = 114, units = "mm")
```

### 4.5.2. Word Clusters
```{r Word Clusters: BusinessTech}
# ggraph visualisation of the correlations and word clusters for the top 20 covid-oriented word pairs
  businessTech_covid_ggraph <- businessTech_covid_cor %>%
    group_by(item1) %>%
    top_n(20) %>%
    ungroup() %>%
    filter(correlation > .15) %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
    geom_node_point(color = "royalblue2", size = 5) +
    geom_node_text(aes(label = name), repel = TRUE) +
    labs(title = "Word clusters", subtitle = "BusinessTech") +
    theme_void() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"))
  
  businessTech_covid_ggraph
  
# Save the graph to disk  
  ggsave(businessTech_covid_ggraph, filename = "businessTech_covid_ggraph.png", width = 185, height = 114, units = "mm")
```
  
## 4.6. Across All Media Outlets

### 4.6.1. Word Pairs
```{r Word Pairs: Compiled Media}
  mediaCompiled_wordPairs <- mediaCompiled %>%
    pairwise_count(word, title, sort = TRUE)

   mediaCompiled_wordPairs
  
# Pairwise correlation
  mediaCompiled_wordPairs_cor <- mediaCompiled %>%
    group_by(word) %>%
    filter(n() >= 20) %>% # Filtering for relatively common words
    pairwise_cor(word, title, sort = TRUE)
  
  mediaCompiled_wordPairs_cor
  
# Filtering for words most associated with the Covid-19 pandemic
  mediaCompiled_covid_cor <- mediaCompiled_wordPairs_cor %>%
    filter(item1 %in% c("ban", "covid", "lockdown")) %>%
    mutate(item2 = reorder(item2, correlation)) 
    
  mediaCompiled_covid_cor
  
# Visualising the 10 most associated words 
  mediaCompiled_covid_cor_visual <-  mediaCompiled_covid_cor %>%
    group_by(item1) %>%
    top_n(10) %>%
    ungroup() %>%
    ggplot(aes(reorder(item2, correlation), correlation)) +
      geom_bar(stat = "identity", fill = "royalblue2") +
      labs(title = "10 most associated words", subtitle = "All media outlets", x = "Associated words") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 12),
            plot.title = element_text(size = 18),
            plot.subtitle = element_text(color = "grey40")) +
      facet_wrap(~item1, scales = "free") +
      coord_flip()
  
  mediaCompiled_covid_cor_visual
  
# Save the graph to disk  
  ggsave(mediaCompiled_covid_cor_visual, filename = "mediaCompiled_covid_cor_visual.png", width = 185, height = 114, units = "mm")
```

### 4.6.2. Word Clusters
```{r Word Clusters: Compiled Media}
# ggraph visualisation of the correlations and word clusters for the top 20 covid-oriented word pairs
  mediaCompiled_covid_ggraph <- mediaCompiled_covid_cor %>%
    group_by(item1) %>%
    top_n(20) %>%
    ungroup() %>%
    filter(correlation > .15) %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
    geom_node_point(color = "royalblue2", size = 5) +
    geom_node_text(aes(label = name), repel = TRUE) +
    labs(title = "Word clusters", subtitle = "All media outlets") +
    theme_void() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"))
  
  mediaCompiled_covid_ggraph
  
# Save the graph to disk  
  ggsave(mediaCompiled_covid_ggraph, filename = "mediaCompiled_covid_ggraph.png", width = 185, height = 114, units = "mm")
```