---
title: "A Computational Analysis of the Business Media's Response to Covid-19: Topic Modelling"
author: "Caryn Biebuyck (20715978) & Lauren Downing (19202113)"
output: html_notebook
---


```{r Setup, message=FALSE, warning=FALSE, include=FALSE}
  library(dplyr)
  library(ggplot2)
  library(ldatuning)
  library(stm)
  library(tidytext)
  library(topicmodels)
```

```{r Reading in required RDS files, message=FALSE, warning=FALSE, include=FALSE}
  fin24 <- readRDS("~/tidy_fin24.rds")
  moneyweb <- readRDS("~/tidy_moneyweb.rds")
  biznews <- readRDS("~/tidy_biznews.rds")
  EWNbusiness <- readRDS("~/tidy_ewn.rds")
  businessTech <- readRDS("~/tidy_businesstech.rds")
  mediaCompiled <- readRDS("~/tidy_mediacompiled.rds")
```


# 1. Creating Document-term Matrices 

## 1.1. Fin24
```{r DTM: Fin24}
# Transforming the data into a DTM
  fin24_dtm <- fin24 %>%
    count(title, word, sort = TRUE) %>%
    cast_dtm(document = title, term = word, value = n)
```

## 1.2. Moneyweb
```{r DTM: Moneyweb}
# Transforming the data into a DTM
  moneyweb_dtm <- moneyweb %>%
    count(title, word, sort = TRUE) %>%
    cast_dtm(document = title, term = word, value = n)
```

## 1.3. BizNews
```{r DTM: BizNews}
# Transforming the data into a DTM
  biznews_dtm <- biznews %>%
    count(title, word, sort = TRUE) %>%
    cast_dtm(document = title, term = word, value = n)
```

## 1.4. EWN Business
```{r DTM: EWN Business}
# Transforming the data into a DTM
  EWNbusiness_dtm <- EWNbusiness %>%
    count(title, word, sort = TRUE) %>%
    cast_dtm(document = title, term = word, value = n)
```

## 1.5. BusinessTech
```{r DTM: BusinessTech}
# Transforming the data into a DTM
  businessTech_dtm <- businessTech %>%
    count(title, word, sort = TRUE) %>%
    cast_dtm(document = title, term = word, value = n)
```

## 1.6. Across All Media Outlets
```{r DTM: All Outlets}
# Transforming the data into a DTM
  mediaCompiled_dtm <- mediaCompiled %>%
    count(title, word, sort = TRUE) %>%
    cast_dtm(document = title, term = word, value = n)
```


# 2. Determining the Optimal Number of Topics (K)
Using the CRAN package [ldatuning]("https://cran.r-project.org/web/packages/ldatuning/vignettes/topics.html") by N. Murzintcev (2020).

## 2.1. Fin24
```{r Determining K: Fin24}
  result <- FindTopicsNumber(
    fin24_dtm,
    topics = seq(from = 2, to = 15, by = 1),
    metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
    method = "Gibbs",
    control = list(seed = 100),
    mc.cores = 2L,
    verbose = FALSE)
  
  FindTopicsNumber_plot(result)
```

## 2.2. Moneyweb
```{r Determining K: Moneyweb}
  result <- FindTopicsNumber(
    moneyweb_dtm,
    topics = seq(from = 2, to = 15, by = 1),
    metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
    method = "Gibbs",
    control = list(seed = 100),
    mc.cores = 2L,
    verbose = FALSE)
  
  FindTopicsNumber_plot(result)
```

## 2.3. BizNews
```{r Determining K: BizNews}
  result <- FindTopicsNumber(
    biznews_dtm,
    topics = seq(from = 2, to = 15, by = 1),
    metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
    method = "Gibbs",
    control = list(seed = 100),
    mc.cores = 2L,
    verbose = FALSE)
  
  FindTopicsNumber_plot(result)
```

## 2.4. EWN Business
```{r Determining K: EWN Business}
  result <- FindTopicsNumber(
    EWNbusiness_dtm,
    topics = seq(from = 2, to = 15, by = 1),
    metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
    method = "Gibbs",
    control = list(seed = 100),
    mc.cores = 2L,
    verbose = FALSE)
  
  FindTopicsNumber_plot(result)
```

## 2.5. BusinessTech
```{r Determining K: BusinessTech}
  result <- FindTopicsNumber(
    businessTech_dtm,
    topics = seq(from = 2, to = 15, by = 1),
    metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
    method = "Gibbs",
    control = list(seed = 100),
    mc.cores = 2L,
    verbose = FALSE)
  
  FindTopicsNumber_plot(result)
```

## 2.6. Across All Media Outlets
```{r Compiled Media: Determining K}
  result <- FindTopicsNumber(
    mediaCompiled_dtm,
    topics = seq(from = 2, to = 15, by = 1),
    metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
    method = "Gibbs",
    control = list(seed = 100),
    mc.cores = 2L,
    verbose = FALSE)
  
  FindTopicsNumber_plot(result)
```

# 3. Latent Dirichlet Allocation (LDA)

## 3.1. Fin24
```{r LDA: Fin24}
# Applying LDA topic modelling
  fin24_lda <- LDA(fin24_dtm, k = 6, control = list(seed = 123))
  
  fin24_lda
  
# Transforming the data into the tidy format
  fin24_lda_td <- tidy(fin24_lda) 
  
  fin24_lda_td
```

### 3.1.1. Top Terms
```{r LDA: Fin24 - Top Terms}
# Top 15 Terms using the `beta` method
  fin24_top_terms <- fin24_lda_td %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    arrange(topic, -beta)
  
# Visualisation
  fin24_top_terms_visual <- fin24_top_terms %>%
    mutate(topic = factor(topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = topic)) +
    geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
    scale_x_reordered() +
    facet_wrap(~topic, scales = "free", ncol = 2) +
    coord_flip()
  
  fin24_top_terms_visual
  
# Save the graph to disk  
  ggsave(fin24_top_terms_visual, filename = "fin24_top_terms_visual.png", width = 185, height = 114, units = "mm")

```

### 3.1.2. Topic Sentiment
```{r LDA: Fin24 - Topic Sentiment}
  fin24_topic_sentiment <- fin24_lda_td %>%
    inner_join(get_sentiments("loughran"), by = c("term" = "word")) %>%
    group_by(topic, sentiment) %>%
    summarise(sentiment_total = sum(beta)) %>%
    mutate(sentiment_ratio = sentiment_total/sum(sentiment_total)) %>%
    ungroup() %>%
    arrange(topic, desc(sentiment_ratio)) %>%
    mutate(sentiment = factor(sentiment))
  
  fin24_topic_sentiment

# Visualisation
  fin24_sentiment_visual <- fin24_topic_sentiment %>%
    ggplot(aes(x = sentiment, y = sentiment_ratio, fill = sentiment)) +
    geom_bar(stat = "identity") +
    labs(x = "", y = "Topic-sentiment Ratio", title = "Topic sentiment of news articles", subtitle = "Fin24") +
    scale_y_continuous(labels = scales::percent) +
    theme_minimal() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"),
          axis.text.x = element_blank()) +
    facet_wrap(~topic) 
    
  fin24_sentiment_visual
  
# Save the graph to disk  
  ggsave(fin24_sentiment_visual, filename = "fin24_sentiment_visual.png", width = 185, height = 114, units = "mm")
```


## 3.2. Moneyweb
```{r LDA: Moneyweb}
# Applying LDA topic modelling
  moneyweb_lda <- LDA(moneyweb_dtm, k = 15, control = list(seed = 123))
  
  moneyweb_lda
  
# Transforming the data into the tidy format
  moneyweb_lda_td <- tidy(moneyweb_lda) 
  
  moneyweb_lda_td
```

### 3.2.1. Top Terms
```{r LDA: Moneyweb - Top Terms}
# Top 15 Terms using the `beta` method
 moneyweb_top_terms <- moneyweb_lda_td %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    arrange(topic, -beta)
  
# Visualisation
  moneyweb_top_terms_visual <- moneyweb_top_terms %>%
    mutate(topic = factor(topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = topic)) +
    geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
    scale_x_reordered() +
    facet_wrap(~topic, scales = "free", ncol = 2) +
    coord_flip()
  
  moneyweb_top_terms_visual

# Save the graph to disk  
  ggsave(moneyweb_top_terms_visual, filename = "moneyweb_top_terms_visual.png", width = 185, height = 254, units = "mm")
```

### 3.2.2. Topic Sentiment
```{r LDA: Moneyweb - Topic Sentiment}
  moneyweb_topic_sentiment <- moneyweb_lda_td %>%
    inner_join(get_sentiments("loughran"), by = c("term" = "word")) %>%
    group_by(topic, sentiment) %>%
    summarise(sentiment_total = sum(beta)) %>%
    mutate(sentiment_ratio = sentiment_total/sum(sentiment_total)) %>%
    ungroup() %>%
    arrange(topic, desc(sentiment_ratio)) %>%
    mutate(sentiment = factor(sentiment))
  
  moneyweb_topic_sentiment

# Visualisation
  moneyweb_sentiment_visual <- moneyweb_topic_sentiment %>%
    ggplot(aes(x = sentiment, y = sentiment_ratio, fill = sentiment)) +
    geom_bar(stat = "identity") +
    labs(x = "", y = "Topic-sentiment Ratio", title = "Topic sentiment of news articles", subtitle = "Moneyweb") +
    scale_y_continuous(labels = scales::percent) +
    theme_minimal() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"),
          axis.text.x = element_blank()) +
    facet_wrap(~topic) 
    
  moneyweb_sentiment_visual
  
# Save the graph to disk  
  ggsave(moneyweb_sentiment_visual, filename = "moneyweb_sentiment_visual.png", width = 185, height = 114, units = "mm")
```

## 3.3. BizNews
```{r LDA: BizNews}
# Applying LDA topic modelling
  biznews_lda <- LDA(biznews_dtm, k = 8, control = list(seed = 123))
  
  biznews_lda
  
# Transforming the data into the tidy format
  biznews_lda_td <- tidy(biznews_lda) 
  
  biznews_lda_td
```

### 3.3.1. Top Terms
```{r LDA: BizNews - Top Terms}
# Top 15 Terms using the `beta` method
 biznews_top_terms <- biznews_lda_td %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    arrange(topic, -beta)
  
# Visualisation
  biznews_top_terms_visual <- biznews_top_terms %>%
    mutate(topic = factor(topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = topic)) +
    geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
    scale_x_reordered() +
    facet_wrap(~topic, scales = "free", ncol = 2) +
    coord_flip()
  
  biznews_top_terms_visual
  
# Save the graph to disk  
  ggsave(biznews_top_terms_visual, filename = "biznews_top_terms_visual.png", width = 185, height = 154, units = "mm")
```

### 3.3.2 Topic Sentiment
```{r LDA: BizNews - Topic Sentiment}
  biznews_topic_sentiment <- biznews_lda_td %>%
    inner_join(get_sentiments("loughran"), by = c("term" = "word")) %>%
    group_by(topic, sentiment) %>%
    summarise(sentiment_total = sum(beta)) %>%
    mutate(sentiment_ratio = sentiment_total/sum(sentiment_total)) %>%
    ungroup() %>%
    arrange(topic, desc(sentiment_ratio)) %>%
    mutate(sentiment = factor(sentiment))
  
  biznews_topic_sentiment

# Visualisation
  biznews_sentiment_visual <- biznews_topic_sentiment %>%
    ggplot(aes(x = sentiment, y = sentiment_ratio, fill = sentiment)) +
    geom_bar(stat = "identity") +
    labs(x = "", y = "Topic-sentiment Ratio", title = "Topic sentiment of news articles", subtitle = "BizNews") +
    scale_y_continuous(labels = scales::percent) +
    theme_minimal() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"),
          axis.text.x = element_blank()) +
    facet_wrap(~topic) 
    
  biznews_sentiment_visual
  
# Save the graph to disk  
  ggsave(biznews_sentiment_visual, filename = "biznews_sentiment_visual.png", width = 185, height = 114, units = "mm")
```

## 3.4. EWN Busines
```{r LDA: EWN Business}
# Applying LDA topic modelling
  EWNbusiness_lda <- LDA(EWNbusiness_dtm, k = 13, control = list(seed = 123))
  
  EWNbusiness_lda
  
# Transforming the data into the tidy format
  EWNbusiness_lda_td <- tidy(EWNbusiness_lda) 
  
  EWNbusiness_lda_td
```

### 3.4.1 Top Terms
```{r LDA: EWN Business - Top Terms}
# Top 15 Terms using the `beta` method
 EWNbusiness_top_terms <- EWNbusiness_lda_td %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    arrange(topic, -beta)
  
# Visualisation
  EWNbusiness_top_terms_visual <- EWNbusiness_top_terms %>%
    mutate(topic = factor(topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = topic)) +
    geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
    scale_x_reordered() +
    facet_wrap(~topic, scales = "free", ncol = 2) +
    coord_flip()
  
  EWNbusiness_top_terms_visual
  
# Save the graph to disk  
  ggsave(EWNbusiness_top_terms_visual, filename = "EWNbusiness_top_terms_visual.png", width = 185, height = 254, units = "mm")
```

### 3.4.2 Topic Sentiment
```{r LDA: EWN Business - Topic Sentiment}
  EWNbusiness_topic_sentiment <- EWNbusiness_lda_td %>%
    inner_join(get_sentiments("loughran"), by = c("term" = "word")) %>%
    group_by(topic, sentiment) %>%
    summarise(sentiment_total = sum(beta)) %>%
    mutate(sentiment_ratio = sentiment_total/sum(sentiment_total)) %>%
    ungroup() %>%
    arrange(topic, desc(sentiment_ratio)) %>%
    mutate(sentiment = factor(sentiment))
  
  EWNbusiness_topic_sentiment

# Visualisation
  EWNbusiness_sentiment_visual <- EWNbusiness_topic_sentiment %>%
    ggplot(aes(x = sentiment, y = sentiment_ratio, fill = sentiment)) +
    geom_bar(stat = "identity") +
    labs(x = "", y = "Topic-sentiment Ratio", title = "Topic sentiment of news articles", subtitle = "EWN Business") +
    scale_y_continuous(labels = scales::percent) +
    theme_minimal() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"),
          axis.text.x = element_blank()) +
    facet_wrap(~topic) 
    
  EWNbusiness_sentiment_visual
  
# Save the graph to disk  
  ggsave(EWNbusiness_sentiment_visual, filename = "EWNbusiness_sentiment_visual.png", width = 185, height = 114, units = "mm")
```

## 3.5. BusinessTech
```{r LDA: BusinessTech}
# Applying LDA topic modelling
  businessTech_lda <- LDA(businessTech_dtm, k = 13, control = list(seed = 123))
  
  businessTech_lda
  
# Transforming the data into the tidy format
  businessTech_lda_td <- tidy(businessTech_lda) 
  
  businessTech_lda_td
```

### 3.5.1 Top Terms
```{r LDA: BusinessTech - Top Terms}
# Top 15 Terms using the `beta` method
 businessTech_top_terms <- businessTech_lda_td %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    arrange(topic, -beta)
  
# Visualisation
  businessTech_top_terms_visual <- businessTech_top_terms %>%
    mutate(topic = factor(topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = topic)) +
    geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
    scale_x_reordered() +
    facet_wrap(~topic, scales = "free", ncol = 2) +
    coord_flip()
  
  businessTech_top_terms_visual
  
# Save the graph to disk  
  ggsave(businessTech_top_terms_visual, filename = "businessTech_top_terms_visual.png", width = 185, height = 254, units = "mm")
```

### 3.5.2 Topic Sentiment
```{r LDA: BusinessTech - Topic Sentiment}
  businessTech_topic_sentiment <- businessTech_lda_td %>%
    inner_join(get_sentiments("loughran"), by = c("term" = "word")) %>%
    group_by(topic, sentiment) %>%
    summarise(sentiment_total = sum(beta)) %>%
    mutate(sentiment_ratio = sentiment_total/sum(sentiment_total)) %>%
    ungroup() %>%
    arrange(topic, desc(sentiment_ratio)) %>%
    mutate(sentiment = factor(sentiment))
  
  businessTech_topic_sentiment

# Visualisation
  businessTech_sentiment_visual <- businessTech_topic_sentiment %>%
    ggplot(aes(x = sentiment, y = sentiment_ratio, fill = sentiment)) +
    geom_bar(stat = "identity") +
    labs(x = "", y = "Topic-sentiment Ratio", title = "Topic sentiment of news articles", subtitle = "BusinessTech") +
    scale_y_continuous(labels = scales::percent) +
    theme_minimal() +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(color = "grey40"),
          axis.text.x = element_blank()) +
    facet_wrap(~topic) 
    
  businessTech_sentiment_visual
  
# Save the graph to disk  
  ggsave(businessTech_sentiment_visual, filename = "businessTech_sentiment_visual.png", width = 185, height = 114, units = "mm")
```

## 3.6. Across All Media Outlets
```{r LDN: Compiled Media}
# Applying LDA topic modelling
  mediaCompiled_lda <- LDA(mediaCompiled_dtm, k = 11, control = list(seed = 123))
  
  mediaCompiled_lda
  
# Transforming the data into the tidy format
  mediaCompiled_lda_td <- tidy(mediaCompiled_lda) 
  
  mediaCompiled_lda_td
```

### 3.6.1 Top Terms
```{r LDN: Compiled Media - Top Terms}
# Top 15 Terms using the `beta` method
  mediaCompiled_top_terms <- mediaCompiled_lda_td %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    arrange(topic, -beta)
  
# Visualisation
  mediaCompiled_top_terms_visual <- mediaCompiled_top_terms %>%
    mutate(topic = factor(topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = topic)) +
    geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
    scale_x_reordered() +
    facet_wrap(~topic, scales = "free", ncol = 2) +
    coord_flip()
  
  mediaCompiled_top_terms_visual
  
# Save the graph to disk  
  ggsave(mediaCompiled_top_terms_visual, filename = "mediaCompiled_top_terms_visual.png", width = 185, height = 234, units = "mm")
```

### 3.6.2 Topic Sentiment
```{r LDN: Compiled Media - Topic Sentiment}
  mediaCompiled_topic_sentiment <- mediaCompiled_lda_td %>%
    inner_join(get_sentiments("loughran"), by = c("term" = "word")) %>%
    group_by(topic, sentiment) %>%
    summarise(sentiment_total = sum(beta)) %>%
    mutate(sentiment_ratio = sentiment_total/sum(sentiment_total)) %>%
    ungroup() %>%
    arrange(topic, desc(sentiment_ratio)) %>%
    mutate(sentiment = factor(sentiment))
  
  mediaCompiled_topic_sentiment

# Visualisation
  mediaCompiled_sentiment_visual <- mediaCompiled_topic_sentiment %>%
    ggplot(aes(x = sentiment, y = sentiment_ratio, fill = sentiment)) +
    geom_bar(stat = "identity") +
    labs(x = "", y = "Topic-sentiment Ratio", title = "Topic sentiment over all news articles") +
    scale_y_continuous(labels = scales::percent) +
    theme_minimal() +
    theme(plot.title = element_text(size = 18),
          axis.text.x = element_blank()) +
    facet_wrap(~topic) 
    
  mediaCompiled_sentiment_visual
  
# Save the graph to disk  
  ggsave(mediaCompiled_sentiment_visual, filename = "mediaCompiled_sentiment_visual.png", width = 185, height = 114, units = "mm")
```

# 4. Structural Topic Modelling (STM)

## 4.1 Fin24
```{r STM: Fin24}
# Transforming the tidied dataset to a document-feature matrix
  fin24_dfm <- fin24 %>%
    count(title, word, sort = TRUE) %>%
    cast_dfm(title, word, n)
  
# Creating a topic model using STM
  fin24_topic_model <- stm(fin24_dfm, K = 6, init.type = "Spectral", verbose = FALSE)

  summary(fin24_topic_model)
```

### 4.1.1. Beta Matrix
```{r STM: Fin24 - Beta Matrix}
  fin24_beta_visual <- tidy(fin24_topic_model) %>%
    group_by(topic) %>%
    top_n(10) %>%
    ungroup() %>%
    mutate(term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(x = term, y = beta, fill = as.factor(topic))) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = "beta", title = "Highest word probabilities for each topic", subtitle = "Fin24")

  fin24_beta_visual
  
# Save the graph to disk  
  ggsave(fin24_beta_visual, filename = "fin24_beta_visual.png", width = 185, height = 114, units = "mm")
```
 
### 4.1.2. Gamma Matrix
```{r STM: Fin24 - Gamma Matrix}
  fin24_gamma_visual <- tidy(fin24_topic_model, matrix = "gamma",
                             document_names = rownames(fin24_dfm)) %>%
    ggplot(aes(x = gamma, fill = as.factor(topic))) +
    geom_histogram(show.legend = FALSE) +
    facet_wrap(~topic, ncol = 2) +
    labs(title = "Distribution of document probabilities for each topic", subtitle = "Fin24")

  fin24_gamma_visual
  
# Save the graph to disk  
  ggsave(fin24_gamma_visual, filename = "fin24_gamma_visual.png", width = 185, height = 114, units = "mm")
```
  
## 4.2. Moneyweb
```{r STM: Moneyweb}
# Transforming the tidied dataset to a document-feature matrix
  moneyweb_dfm <- moneyweb %>%
    count(title, word, sort = TRUE) %>%
    cast_dfm(title, word, n)

# Creating a topic model using STM
  moneyweb_topic_model <- stm(moneyweb_dfm, K = 15, init.type = "Spectral", verbose = FALSE)
  
  summary(moneyweb_topic_model)
```
  
### 4.2.1. Beta Matrix
```{r STM: Moneyweb - Beta Matrix}
  moneyweb_beta_visual <- tidy(moneyweb_topic_model) %>%
    group_by(topic) %>%
    top_n(10) %>%
    ungroup() %>%
    mutate(term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(x = term, y = beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = "beta", title = "Highest word probabilities for each topic", subtitle = "Moneyweb")

  moneyweb_beta_visual
  
# Save the graph to disk  
  ggsave(moneyweb_beta_visual, filename = "moneyweb_beta_visual.png", width = 185, height = 154, units = "mm")
```
  
### 4.2.2. Gamma Matrix
```{r STM: Moneyweb - Gamma}
  moneyweb_gamma_visual <- tidy(moneyweb_topic_model, matrix = "gamma",
                                document_names = rownames(moneyweb_dfm)) %>%
    ggplot(aes(gamma, fill = as.factor(topic))) +
    geom_histogram(show.legend = FALSE) +
    facet_wrap(~topic, ncol = 2) +
    labs(title = "Distribution of document probabilities for each topic", subtitle = "Moneyweb")

  moneyweb_gamma_visual
  
# Save the graph to disk  
  ggsave(moneyweb_gamma_visual, filename = "moneyweb_gamma_visual.png", width = 185, height = 254, units = "mm")
```
  
## 4.3. BizNews
```{r STM: BizNews}
 # Transforming the tidied dataset to a document-feature matrix
  biznews_dfm <- biznews %>%
    count(title, word, sort = TRUE) %>%
    cast_dfm(title, word, n)

# Creating a topic model using STM
  biznews_topic_model <- stm(biznews_dfm, K = 8, init.type = "Spectral", verbose = FALSE)
  
  summary(biznews_topic_model)
```
  
### 4.3.1. Beta Matrix
```{r STM: BizNews - Beta Matrix}
  biznews_beta_visual <- tidy(biznews_topic_model) %>%
    group_by(topic) %>%
    top_n(10) %>%
    ungroup() %>%
    mutate(term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(x = term, y = beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = "beta", title = "Highest word probabilities for each topic", subtitle = "BizNews")

  biznews_beta_visual
  
# Save the graph to disk  
  ggsave(biznews_beta_visual, filename = "biznews_beta_visual.png", width = 185, height = 114, units = "mm")
```

### 4.3.2. Gamma Matrix
```{r STM: BizNews - Gamma Matrix}
  biznews_gamma_visual <- tidy(biznews_topic_model, matrix = "gamma",
                               document_names = rownames(biznews_dfm)) %>%
    ggplot(aes(gamma, fill = as.factor(topic))) +
    geom_histogram(show.legend = FALSE) +
    facet_wrap(~topic, ncol = 3) +
    labs(title = "Distribution of document probabilities for each topic", subtitle = "BizNews")

  biznews_gamma_visual
  
# Save the graph to disk  
  ggsave(biznews_gamma_visual, filename = "biznews_gamma_visual.png", width = 185, height = 114, units = "mm")
```

## 4.4. EWN Business
```{r STM: EWN Business}
 # Transforming the tidied dataset to a document-feature matrix
  EWNbusiness_dfm <- EWNbusiness %>%
    count(title, word, sort = TRUE) %>%
    cast_dfm(title, word, n)

# Creating a topic model using stm
  EWNbusiness_topic_model <- stm(EWNbusiness_dfm, K = 10, init.type = "Spectral", verbose = FALSE)
  
  summary(EWNbusiness_topic_model)
```
  
### 4.4.1. Beta Matrix
```{r STM: EWN Business - Beta Matrix}
  EWNbusiness_beta_visual <- tidy(EWNbusiness_topic_model) %>%
    group_by(topic) %>%
    top_n(10) %>%
    ungroup() %>%
    mutate(term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(x = term, y = beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = "beta", title = "Highest word probabilities for each topic", subtitle = "EWN Business")

  EWNbusiness_beta_visual
  
# Save the graph to disk  
  ggsave(EWNbusiness_beta_visual, filename = "EWNbusiness_beta_visual.png", width = 185, height = 114, units = "mm")
```
 
### 4.4.2. Gamma Matrix
```{r STM: EWN Business - Gamma Matrix}
  EWNbusiness_gamma_visual <- tidy(EWNbusiness_topic_model, matrix = "gamma",
                               document_names = rownames(EWNbusiness_dfm)) %>%
    ggplot(aes(gamma, fill = as.factor(topic))) +
    geom_histogram(show.legend = FALSE) +
    facet_wrap(~topic, ncol = 3) +
    labs(title = "Distribution of document probabilities for each topic", subtitle = "EWN Business")

  EWNbusiness_gamma_visual
  
# Save the graph to disk  
  ggsave(EWNbusiness_gamma_visual, filename = "EWNbusiness_gamma_visual.png", width = 185, height = 114, units = "mm")
```

## 4.5. BusinessTech
```{r STM: BusinessTech}
# Transforming the tidied dataset to a document-feature matrix
  businessTech_dfm <- businessTech %>%
    count(title, word, sort = TRUE) %>%
    cast_dfm(title, word, n)

# Creating a topic model using stm
  businessTech_topic_model <- stm(businessTech_dfm, K = 13, init.type = "Spectral", verbose = FALSE)
  
  summary(businessTech_topic_model)
```
 
### 4.5.1. Beta Matrix
```{r STM: BusinessTech - Beta Matrix}
  businessTech_beta_visual <- tidy(businessTech_topic_model) %>%
    group_by(topic) %>%
    top_n(10) %>%
    ungroup() %>%
    mutate(term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(x = term, y = beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = "beta", title = "Highest word probabilities for each topic", subtitle = "BusinessTech")

  businessTech_beta_visual
  
# Save the graph to disk  
  ggsave(businessTech_beta_visual, filename = "businessTech_beta_visual.png", width = 185, height = 154, units = "mm")
```

### 4.5.2. Gamma Matrix
```{r STM: BusinessTech - Gamma Matrix}
  businessTech_gamma_visual <- tidy(businessTech_topic_model, matrix = "gamma",
                               document_names = rownames(businessTech_dfm)) %>%
    ggplot(aes(gamma, fill = as.factor(topic))) +
    geom_histogram(show.legend = FALSE) +
    facet_wrap(~topic, ncol = 3) +
    labs(title = "Distribution of document probabilities for each topic", subtitle = "BusinessTech")

  businessTech_gamma_visual
  
# Save the graph to disk  
  ggsave(businessTech_gamma_visual, filename = "businessTech_gamma_visual.png", width = 185, height = 134, units = "mm")
```

## 4.6. Across All Media Outlets
```{r STM: Compiled Media}
# Transforming the tidied dataset to a document-feature matrix
  mediaCompiled_dfm <- mediaCompiled %>%
    count(title, word, sort = TRUE) %>%
    cast_dfm(title, word, n)

# Creating a topic model using stm
  mediaCompiled_topic_model <- stm(mediaCompiled_dfm, K = 11, init.type = "Spectral", verbose = FALSE)
  
  summary(mediaCompiled_topic_model)
```

### 4.6.1. Beta Matrix 
```{r STM: Compiled Media - Beta Matrix}
  mediaCompiled_beta_visual <- tidy(mediaCompiled_topic_model) %>%
    group_by(topic) %>%
    top_n(10) %>%
    ungroup() %>%
    mutate(term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(x = term, y = beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = "beta", title = "Highest word probabilities for each topic", subtitle = "All media outlets")

  mediaCompiled_beta_visual
  
# Save the graph to disk  
  ggsave(mediaCompiled_beta_visual, filename = "mediaCompiled_beta_visual.png", width = 185, height = 114, units = "mm")
```
  
### 4.6.2. Gamma Matrix 
```{r STM: Compiled Media - Gamma Matrix}
  mediaCompiled_gamma_visual <- tidy(mediaCompiled_topic_model, matrix = "gamma",
                               document_names = rownames(mediaCompiled_dfm)) %>%
    ggplot(aes(gamma, fill = as.factor(topic))) +
    geom_histogram(show.legend = FALSE) +
    facet_wrap(~topic, ncol = 3) +
    labs(title = "Distribution of document probabilities for each topic", subtitle = "All media outlets")

  mediaCompiled_gamma_visual
  
# Save the graph to disk  
  ggsave(mediaCompiled_gamma_visual, filename = "mediaCompiled_gamma_visual.png", width = 185, height = 114, units = "mm")
```